---
title: "index"
author: "ADG"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(lubridate)
library(DT)

data_path <- "data"   # path to the data
files <- dir(data_path, pattern = "\\.csv$", full.names = TRUE)

READ <- function(FILE) {
  read_csv(FILE,
           trim_ws = TRUE,
           guess_max = nrow(read_csv(FILE)) -12,
           n_max = nrow(read_csv(FILE)) -12,
           col_types = cols(
           )) %>% 
    rename_all(make.names) %>% 
    mutate(., filename = FILE) 
}

data <- files %>%
  map(READ) %>%    # read in all the files individually, using
  # the function READ from above
  reduce(full_join) # reduce with full_join into one dataframe



write_csv(data, "data_combined.csv")


```

## Initial Results

We look up the ownership information for the 19 publicly traded firms tracked by AFSC. We combined the data above for the firms. 

Here we limit the results to include only "Mutual Fund" products that are domiciled in the "United States" as captured by Morningstar Direct.

We further limit the results to only include those with a Fund Legal Structure of "Closed Ended Investment Company" or "Open Ended Investment Company".

```{r results}


results <- data %>% 
  mutate(Stock = str_replace(filename, "data/MD.", ""),
         Stock = str_replace(Stock, "(_..csv)|(_ADR.csv)", "")
           ) %>% 
  select(Name, Stock, FundId, everything()) %>% 
  filter((Portfolio..Owner.Type == "Mutual Fund" & Domicile == "United States") |
           !is.na(FundId) & is.na(Portfolio..Owner.Type) & Domicile == "United States")

results <- results %>% 
  filter(Stock != "BAESystems_BAESY",
         Fund.Legal.Structure %in% c("Closed Ended Investment Company", "Open Ended Investment Company") | is.na(Fund.Legal.Structure))

write_csv(results, "results.csv")

```

## Getting the fund IDs

For the above funds we pull unique FundIDs in the dataset to match with data from Morningstar Direct


```{r ids, echo=FALSE}

fundid_present <- results %>% 
  group_by(Portfolio..Owner.Type, FundId) %>% 
  mutate(Blank = case_when(
    is.na(FundId) ~ "blank",
    !is.na(FundId) ~ "present"
  )) %>% 
  group_by(Domicile, Portfolio..Owner.Type, Blank) %>% 
  count()

fundid_blank <- results %>% 
  filter(is.na(FundId))

fundids <- results %>% 
  filter(!is.na(FundId)) %>% 
  select(FundId) %>% 
  distinct() %>% 
  write_csv(., "fundids.csv")


```

##Pairing ownership data with fund info
Using the FundIDs captured above we use the Morningstar Direct database to capture a list of correspoinding funds in the open-end fund section of Direct.

Morningstar flagged it was unable to directly find matches in 61 instances. In those cases I manually searched for each fund. Where possible, missing_matched.csv resolves those cases.

The end result here is to combine the funds found in Morninstar's portfolio ownership section with their corresponding data from the open-end fund section.

```{r share_data, echo=FALSE}

share_data <- results %>% 
  select(1:82) %>% 
  filter(!is.na(FundId)) %>% 
  distinct()


data_path <- "matches"   # path to the data
files <- dir(data_path, pattern = "\\.csv$", full.names = TRUE)

matches <- files %>% 
  map(READ) %>%    # read in all the files individually, using
  # the function READ from above
  reduce(full_join) # reduce with full


matches1 <- matches %>% 
  select(1:78) %>% 
  distinct()

missing_identified <- read_csv("missing_matched.csv")

matches2 <- left_join(matches1, missing_identified, by = "Name") %>% 
  mutate(ID =
           case_when(
             !is.na(ID) ~ ID,
             is.na(ID) ~ FundId
           ))


join <- left_join(share_data, matches2, by = c("FundId"="ID"))

missing <- join %>%
  filter(is.na(Name.y))

```

##Working data

Once we have combined the data we remove those with an Investment Type of "Insurance Product Fund"

We also link affiliated fund shops with Branding.Name.Mod to account for some mergers and acquisitions 

```{r conflicts}

conflicts <- join %>% 
  filter(Investment.Type.y != "Insurance Product Fund" | is.na(Investment.Type.y),
         !is.na(Name.y)) %>% 
  mutate(
    Branding.Name.Mod =
      case_when(
        grepl("State Street", Branding.Name) ~ "State Street",
        grepl("TIAA", Branding.Name) ~ "TIAA/Nuveen",
        grepl("Nuveen", Branding.Name) ~ "TIAA/Nuveen",
        grepl("Eaton Vance", Branding.Name) ~ "Morgan Stanley",
        grepl("Calvert", Branding.Name) ~ "Eaton Vance/Calvert",
        grepl("iShares", Branding.Name) ~ "iShares/BlackRock",
        grepl("BlackRock", Branding.Name) ~ "iShares/BlackRock",
        grepl("PowerShares", Branding.Name) ~ "PowerShares/Invesco",
        grepl("Invesco", Branding.Name) ~ "PowerShares/Invesco",
        grepl("DWS$", Branding.Name) ~ "DWS/Xtrackers",
        grepl("Xtrackers", Branding.Name) ~ "DWS/Xtrackers",
        grepl("^Capital Group", Branding.Name) ~ "American Funds",
        Branding.Name %in% c("Harding Loevner", "Third Avenue",
                             "Tweedy, Browner") ~ "AMG",
        Branding.Name == "Oppenheimer" ~ "PowerShares/Invesco",
        Branding.Name == "Wells Fargo" ~ "Allspring",
        Branding.Name %in% "Amundi" ~ "Pioneer Investments",
        TRUE ~ Branding.Name
      ))


write_csv(conflicts, "conflicts.csv")

```

## Assets in 19 firms across all shops

Here we see assets held in the 19 firms at each fund shop. This includes index funds.


```{r all_shops_assets}

all_shops_assets <- conflicts %>% 
  filter(Fund.of..Funds == "No") %>% 
  group_by(Branding.Name.Mod) %>% 
  summarise(Total_March24 = sum(Position.Market.Value..2024.03..USD, na.rm = T)) %>% 
  arrange(desc(Total_March24))

datatable(all_shops_assets)

```


## Count of funds invested in any of the 19 firms across all shops

Here we see the number of funds at each shops that hold at least one the 19 firms. This includes index funds.

```{r all_shops_count}

all_shops_count <- conflicts %>% 
  filter(Fund.of..Funds == "No") %>% 
  group_by(Branding.Name.Mod, FundId) %>% 
  summarise(Funds = n()) %>% 
  group_by(Branding.Name.Mod) %>% 
  summarise(Funds_March24 = n()) %>% 
  arrange(desc(Funds_March24))

datatable(all_shops_count)

```
## Assets in 19 firms across ACTIVE shops

Here we see assets held in the 19 firms at each fund shop. This includes ONLY active funds.


```{r active_shops_assets}

active_shops_assets <- conflicts %>% 
  filter(Fund.of..Funds == "No") %>% 
  filter(Index..Fund == "No") %>% 
  group_by(Branding.Name.Mod) %>% 
  summarise(Total_March24 = sum(Position.Market.Value..2024.03..USD, na.rm = T)) %>% 
  arrange(desc(Total_March24))

datatable(active_shops_assets)

```

## Count of funds invested in any of the 19 firms across ACTIVE shops
Here we see the number of funds at each shop that hold at least one the 19 firms. This includes ONLY active funds.



```{r active_shops_count}

active_shops_count <- conflicts %>%
  filter(Fund.of..Funds == "No") %>% 
  filter(Index..Fund == "No") %>% 
  group_by(Branding.Name.Mod, FundId) %>% 
  summarise(Funds = n()) %>% 
  group_by(Branding.Name.Mod) %>% 
  summarise(Funds_March24 = n()) %>% 
  arrange(desc(Funds_March24))

datatable(active_shops_count)

```

##Stocks
This checks we have not double counted any funds holding the same firms. This is a possibility because during the data pull step we pulled various versions of the 19 firms such as domestic and international stock symbols in Direct.

```{r stocks}


stock <- conflicts %>%
  mutate(Stock_Clean =
           case_when(grepl("Royce", Stock) ~ "Rolls Royce",
         TRUE ~ Stock)) %>% 
  group_by(Stock_Clean, Index..Fund) %>%
  count(name = "Total") %>% 
  pivot_wider(
    names_from = Index..Fund,
    values_from = Total
  )


```


##Largest funds
At shop levels at least $1B as of September in the 19 for onlyc active funds.

No == Non-esg
Yes == ESG
NA == Morningstar doesn't classify
Total is sum all of the above

```{r largest_companies}

largest <- conflicts %>% 
  filter(Index..Fund == "No") %>%
  group_by(Branding.Name.Mod,Sustainable.Investment.Overall..2024.03) %>% 
  summarise(Assets_in_19_q3 = sum(Position.Market.Value..2023.09..USD, na.rm = T)) %>% 
  pivot_wider(
    names_from = Sustainable.Investment.Overall..2024.03,
    values_from = Assets_in_19_q3
  ) %>% 
  group_by(Branding.Name.Mod) %>% 
  mutate(Total = sum(Yes, No, `NA`, na.rm = T)) %>% 
  arrange(desc(Total))



```


tktktk


```{r stock_assets}



stock_assets <- conflicts %>%
  mutate(Stock_Clean =
           case_when(grepl("Royce", Stock) ~ "Rolls Royce",
                     TRUE ~ Stock)) %>% 
  group_by(Stock_Clean, Index..Fund) %>%
  summarise(Total = sum(Position.Market.Value..2024.03..USD, na.rm = T)) %>% 
  pivot_wider(
    names_from = Index..Fund,
    values_from = Total
  )


```

## Shares held by all funds Active vs. Index

tktkktk

```{r shares}


shares <- conflicts %>% 
  group_by(Index..Fund) %>% 
  summarise(
    `Q1 2023` = sum(Shares..2023.03, na.rm = T),
    `Q2 2023` = sum(Shares..2023.06, na.rm = T),
    `Q3 2023` = sum(Shares..2023.09, na.rm = T),
    `Q4 2023` = sum(Shares..2023.12, na.rm = T),
    `Q1 2024` = sum(Shares..2024.03, na.rm = T)
  ) %>% 
  mutate(
    change = 
      (`Q1 2024`-`Q3 2023`)/`Q3 2023`*100
  ) %>% 
  arrange(desc(change))

datatable(shares)


```

## Shares held by all ACTIVE funds ESG vs. non-ESG


```{r shares_activeESG}


shares_activeESG <- conflicts %>% 
  filter(Index..Fund == "No") %>%
  group_by(Sustainable.Investment.Overall..2024.03) %>% 
  summarise(
    `Q1 2023` = sum(Shares..2023.03, na.rm = T),
    `Q2 2023` = sum(Shares..2023.06, na.rm = T),
    `Q3 2023` = sum(Shares..2023.09, na.rm = T),
    `Q4 2023` = sum(Shares..2023.12, na.rm = T),
    `Q1 2024` = sum(Shares..2024.03, na.rm = T)
  ) %>% 
  mutate(
    change = 
      (`Q1 2024`-`Q3 2023`)/`Q3 2023`*100
  ) %>% 
  arrange(desc(change))

datatable(shares_activeESG)


```


## Change in shares held by Active Funds


```{r shares_activeESGfunds}


shares_activeESGfunds <- conflicts %>% 
    filter(Index..Fund == "No") %>%
    group_by(Name.x, Sustainable.Investment.Overall..2024.03) %>% 
  summarise(
    `Q1 2023` = sum(Shares..2023.03, na.rm = T),
    `Q2 2023` = sum(Shares..2023.06, na.rm = T),
    `Q3 2023` = sum(Shares..2023.09, na.rm = T),
    `Q4 2023` = sum(Shares..2023.12, na.rm = T),
    `Q1 2024` = sum(Shares..2024.03, na.rm = T)
  )  %>% 
  mutate(
    change = 
      (`Q1 2024`-`Q3 2023`)/`Q3 2023`*100
  ) %>% 
  arrange(desc(change))

datatable(shares_activeESGfunds)


```


## Change in shares held by Shops that held the most assets of the 19 as of Sept. 30


cap is $1B
includes all funds passive and active 

```{r shares_activeESGShops}

toplargest <- largest %>% 
  ungroup() %>% 
  filter(total>=1000000000)

  shares_activeShops <- conflicts %>% 
    filter(
      Branding.Name.Mod %in% top20$Branding.Name.Mod,
      Index..Fund == "No") %>%
    group_by(Branding.Name.Mod) %>% 
  summarise(
    `Q1 2023` = sum(Shares..2023.03, na.rm = T),
    `Q2 2023` = sum(Shares..2023.06, na.rm = T),
    `Q3 2023` = sum(Shares..2023.09, na.rm = T),
    `Q4 2023` = sum(Shares..2023.12, na.rm = T),
    `Q1 2024` = sum(Shares..2024.03, na.rm = T)
    ) %>% 
  mutate(
    change = 
      (`Q1 2024`-`Q3 2023`)/`Q3 2023`*100
  ) %>% 
  arrange(desc(change))

datatable(shares_activeShops)


```
